---
format:
  gfm:
    wrap: preserve
knitr:
  opts_chunk:
    collapse: true
    comment: "#>"
    fig.path: "man/figures/README-"
    out.width: "100%"
---

<!-- README.md is generated from README.qmd. Please edit that file -->

# checklist

<!-- badges: start -->
[![R-CMD-check](https://github.com/rundel/checklist/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/rundel/checklist/actions/workflows/R-CMD-check.yaml)
[![pkgdown](https://github.com/rundel/checklist/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/rundel/checklist/actions/workflows/pkgdown.yaml)
<!-- badges: end -->

checklist provides tools for instructors to automatically check the structure and reproducibility of student assignment submissions.
The goal is not to check an assignment for correctness, but rather that the submission is complete, well-formed, and reproducible.
The package includes checks for:

* required, allowed, and disallowed files
* required, allowed, and disallowed package dependencies
* successful rendering of R Markdown and Quarto documents

Checks can be run locally or, more usefully, automatically against each student submission using GitHub Actions or a similar continuous integration service.


## Installation

<!--
You can install the released version of checklist from [CRAN](https://CRAN.R-project.org) with:
``` r
install.packages("checklist")
```
-->

You can install the development version of this package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rundel/checklist")
```

## Example

```{r}
library(checklist)
```

Let's look at a simple example of the type of assignment a student might turn in.
All of the files are available in `inst/examples/hw1` within this repository.
If you have already installed the package then the directory can also be found using `system.file("examples/hw1", package="checklist")`.

```{r}
dir = system.file("examples/hw1", package="checklist")

# Show the project contents
fs::dir_tree("inst/examples/hw1")
```

We can now use checklist to express simple checks for the files in this directory.
For example, if we wanted to make sure that the students submit a rendered version of their homework we could use the following check:

```{r}
check_required_files("hw1.md", dir)
```

Alternatively, we may want to prevent the students from turning in a rendered version (to check the reproducibility of their work) and this can be done explicitly with

```{r}
check_disallowed_files("hw1.md", dir)
```

We may instead want to be explicit about which files are allowed, ensuring students have not added or renamed anything:

```{r}
check_allowed_files(c("README.md", "hw1.qmd", "hw1.Rproj"), dir)
```

By default the package ignores hidden files (files whose name starts with a `.`).
These can be included in the checks using the `all = TRUE` argument.

```{r}
check_allowed_files(c("README.md", "hw1.qmd", "hw1.Rproj"), dir, all = TRUE)
```

To refine this, we may want to allow `.gitignore` as well as the `.Rproj.user/` folder.
These can be added to the files argument, and standard glob wildcards are supported to make our life easier:

```{r}
check_allowed_files(
  c("README.md", "hw1.qmd", "hw1.Rproj", ".gitignore", ".Rproj.user/*"),
  dir, all = TRUE
)
```

## Using with GitHub Actions

These checks are most useful when they run automatically against student submissions, for example via a GitHub Actions workflow in each student's repository.
`quit_on_failure()` ensures that a failed check also fails the workflow run.
An example workflow for the `hw1` assignment above ships with the package in `templates/check_assignment.yml`, which can be located with `system.file("templates/check_assignment.yml", package = "checklist")`.
It can be copied into an assignment repository as `.github/workflows/check_assignment.yml`:

``` yaml
{{< include inst/templates/check_assignment.yml >}}
```
